---
title: "FedData Play"
output: html_notebook
---

PURPOSE: This script is to play and practice with the FedData package

APPROACH
1) https://github.com/ropensci/FedData Use this demo to explore functionalities

```{r}
# FedData Tester
library(FedData)
library(magrittr)

# Extract data for Mesa Verde National Park:
vepPolygon <- polygon_from_extent(raster::extent(672800, 740000, 4102000, 4170000),
  proj4string = "+proj=utm +datum=NAD83 +zone=12"
)

```

Get and plot National Elevation dataset for the study area
```{r}
# Get the NED (USA ONLY)
# Returns a raster
NED <- get_ned(
  template = vepPolygon,
  label = "VEPIIN"
)
#> Warning in showSRID(uprojargs, format = "PROJ", multiline = "NO"): Discarded
#> datum Unknown based on WGS84 ellipsoid in CRS definition
# Plot with raster::plot
raster::plot(NED)

```

Get and plot the Daymet dataset for the study area
```{r}
# Get the DAYMET (North America only)
# Returns a raster
DAYMET <- get_daymet(
  template = vepPolygon,
  label = "VEPIIN",
  elements = c("prcp", "tmax"),
  years = 1980:1985
)
# Plot with raster::plot
raster::plot(DAYMET$tmax$X1985.10.23)

```

Get and plot the daily GHCN precipitation data for the study area
```{r}
# Get the daily GHCN data (GLOBAL)
# Returns a list: the first element is the spatial locations of stations,
# and the second is a list of the stations and their daily data
GHCN.prcp <- get_ghcn_daily(
  template = vepPolygon,
  label = "VEPIIN",
  elements = c("prcp")
)
#> Warning: `select_()` is deprecated as of dplyr 0.7.0.
#> Please use `select()` instead.
#> This warning is displayed once every 8 hours.
#> Call `lifecycle::last_warnings()` to see where this warning was generated.
# Plot the NED again
raster::plot(NED)
# Plot the spatial locations
sp::plot(GHCN.prcp$spatial,
  pch = 1,
  add = TRUE
)
legend("bottomleft",
  pch = 1,
  legend = "GHCN Precipitation Records"
)

```

Get and plot the daily GHCN temperature data for the study area
```{r}
# Elements for which you require the same data
# (i.e., minimum and maximum temperature for the same days)
# can be standardized using standardize==T
GHCN.temp <- get_ghcn_daily(
  template = vepPolygon,
  label = "VEPIIN",
  elements = c("tmin", "tmax"),
  years = 1980:1985,
  standardize = TRUE
)
#> Warning: `filter_()` is deprecated as of dplyr 0.7.0.
#> Please use `filter()` instead.
#> See vignette('programming') for more help
#> This warning is displayed once every 8 hours.
#> Call `lifecycle::last_warnings()` to see where this warning was generated.
# Plot the NED again
raster::plot(NED)
# Plot the spatial locations
sp::plot(GHCN.temp$spatial,
  add = TRUE,
  pch = 1
)
legend("bottomleft",
  pch = 1,
  legend = "GHCN Temperature Records"
)
```

Get and plot the National Hydrography data set for the study area
```{r}
# Get the NHD (USA ONLY)
get_nhd(
  template = FedData::glac,
  label = "glac"
) %>%
  plot_nhd(template = FedData::glac)

```

Get and plot the NRCS SSURGO data for the study area
```{r}
# Get the NRCS SSURGO data (USA ONLY)
SSURGO.VEPIIN <- get_ssurgo(
  template = vepPolygon,
  label = "VEPIIN"
)
# Plot the NED again
raster::plot(NED)
# Plot the SSURGO mapunit polygons
plot(SSURGO.VEPIIN$spatial,
  lwd = 0.1,
  add = TRUE
)
```

Get and plot the NRCS SSURGO data for particular soil survey areas
```{r}
# Or, download by Soil Survey Area names
SSURGO.areas <- get_ssurgo(
  template = c("CO670", "CO075"),
  label = "CO_TEST"
)

# Let's just look at spatial data for CO675
SSURGO.areas.CO675 <-
  SSURGO.areas$spatial %>%
  dplyr::filter(AREASYMBOL == "CO075")

# And get the NED data under them for pretty plotting
NED.CO675 <- get_ned(
  template = SSURGO.areas.CO675,
  label = "SSURGO_CO675"
)
#> Warning in if (class(x) != "extent") {: the condition has length > 1 and only
#> the first element will be used
#> Warning in showSRID(uprojargs, format = "PROJ", multiline = "NO"): Discarded
#> datum Unknown based on WGS84 ellipsoid in CRS definition

# Plot the SSURGO mapunit polygons, but only for CO675
plot(NED.CO675)
plot(SSURGO.areas.CO675,
  lwd = 0.1,
  add = TRUE
)
#> Warning in plot.sf(SSURGO.areas.CO675, lwd = 0.1, add = TRUE): ignoring all but
#> the first attribute


```

Get and plot the ITRDB chronology locations in the study area
```{r}
# Get the ITRDB records
ITRDB <- get_itrdb(
  template = vepPolygon,
  label = "VEPIIN",
  recon.years = 850:2000,
  calib.years = 1924:1983,
  measurement.type = "Ring Width",
  chronology.type = "ARSTND"
)
#> Warning in eval(jsub, SDenv, parent.frame()): NAs introduced by coercion
#> Warning: attribute variables are assumed to be spatially constant throughout all
#> geometries

# Plot the NED again
raster::plot(NED)
# Map the locations of the tree ring chronologies
plot(ITRDB$metadata$geometry,
  pch = 1,
  add = TRUE
)
legend("bottomleft",
  pch = 1,
  legend = "ITRDB chronologies"
)
```

Get and plot the National Land Cover dataset for the study area
```{r}
# Get the NLCD (USA ONLY)
# Returns a raster
NLCD <- get_nlcd(
  template = vepPolygon,
  year = 2016,
  dataset = "Land_Cover",
  label = "VEPIIN"
)
#> Warning in showSRID(uprojargs, format = "PROJ", multiline = "NO"): Discarded
#> ellps WGS 84 in CRS definition: +proj=merc +a=6378137 +b=6378137 +lat_ts=0
#> +lon_0=0 +x_0=0 +y_0=0 +k=1 +units=m +nadgrids=@null +wktext +no_defs
#> Warning in showSRID(uprojargs, format = "PROJ", multiline = "NO"): Discarded
#> datum WGS_1984 in CRS definition
# Plot with raster::plot
raster::plot(NLCD)

```

```{r}
# You can also download the Canopy (2011 only) or impervious datasets:
NLCD_canopy <- get_nlcd(
  template = vepPolygon,
  year = 2011,
  dataset = "Tree_Canopy",
  label = "VEPIIN"
)
#> Warning in showSRID(uprojargs, format = "PROJ", multiline = "NO"): Discarded
#> ellps WGS 84 in CRS definition: +proj=merc +a=6378137 +b=6378137 +lat_ts=0
#> +lon_0=0 +x_0=0 +y_0=0 +k=1 +units=m +nadgrids=@null +wktext +no_defs

#> Warning in showSRID(uprojargs, format = "PROJ", multiline = "NO"): Discarded
#> datum WGS_1984 in CRS definition
# Plot with raster::plot
raster::plot(NLCD_canopy)


```

```{r}
NLCD_impervious <- get_nlcd(
  template = vepPolygon,
  year = 2016,
  dataset = "Impervious",
  label = "VEPIIN"
)
#> Warning in showSRID(uprojargs, format = "PROJ", multiline = "NO"): Discarded
#> ellps WGS 84 in CRS definition: +proj=merc +a=6378137 +b=6378137 +lat_ts=0
#> +lon_0=0 +x_0=0 +y_0=0 +k=1 +units=m +nadgrids=@null +wktext +no_defs

#> Warning in showSRID(uprojargs, format = "PROJ", multiline = "NO"): Discarded
#> datum WGS_1984 in CRS definition
# Plot with raster::plot
raster::plot(NLCD_impervious)

```

Get and plot the NASS Cropland data layer for the study area
```{r}
# Get the NASS (USA ONLY)
# Returns a raster
NASS <- get_nass(
  template = vepPolygon,
  year = 2016,
  label = "VEPIIN"
)
# Plot with raster::plot
raster::plot(NASS)


```


```{r}
# Get the NASS classification table
raster::levels(NASS)[[1]]

```

