---
title: "Autocorrelation - Assignment"
output: html_notebook
---

Q3. Time Series Plot with mean line
  PLUS extra code for
      1) exp white noise 
      2) random walk code
```{r}
# Generate time series
n  <- 100   # length of time series
m  <- 0     # series mean
sd <- 1     # series standard deviation

# Code below from Bookdown/Napier 
# Gaussian
Norm_white_noise <- rnorm(n)
mean_line <- rep(m,n)
# Exponential 
Exp_white_noise <- rexp(n)
# Random walk
Norm_ran_walk <- rep(0,n) # Gaussian
Exp_ran_walk <- rep(0,n)

for (i in 2:n) {
  Norm_ran_walk[i] <- Norm_ran_walk[(i-1)] + rnorm(1)
  Exp_ran_walk[i] <- Exp_ran_walk[(i-1)] + rexp(1)
}

# moving average
Norm_mov_avg <- filter(Norm_white_noise,sides=2,rep(1/3,3))  #TAS+Apps: 13

plot(Norm_white_noise, type="o")
lines(mean_line)

plot(Norm_mov_avg, type="o")
lines(mean_line)
```

Q4. Zoom in on TS; highlighted two data points that would contribute to negative lag-1 ac
There are two sections requiring User input: 
1) Selection of sub-period
2) Selection of years exhibiting lag1 behavior
```{r}
##################################################################
# Select your sub-period
start_sub <- 40
end_sub <- 70

# Enter the years that exhibit potential lag1 behavior
lag1_years = c(46,47,48)
##################################################################

# Plot a subperiod of the times series
plot(Norm_white_noise, type="o",xlim=c(start_sub,end_sub))
lines(mean_line)

# Highlight lag1 years
points(lag1_years[1],Norm_white_noise[lag1_years[1]],pch=17, col="red",cex=1.5)
points(lag1_years[2],Norm_white_noise[lag1_years[2]],pch=17, col="red",cex=1.5)
points(lag1_years[3],Norm_white_noise[lag1_years[3]],pch=17, col="red",cex=1.5)
```

Q5. Lagged scatterplots, lags 1-4
```{r}

```

Q6. ACF
```{r}

```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
